---
title: 'Regulation of pupil size in natural vision - hypotheses'
date: "`r format(Sys.Date(), format = '%d %b %Y')`"
output:
  html_document:
    df_print: paged
    code_folding: show
    keep_md: no
    number_sections: yes
    toc: yes
    toc_depth: 5
    toc_float: yes
  pdf_document:
    number_sections: yes
editor_options:
  chunk_output_type: console
---

```{r, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 5, echo = TRUE, eval = TRUE, message = TRUE, warning = FALSE, error = TRUE, cache = FALSE, cache.path = "cache/", cache.extra = 1, fig.path = paste0("figures/", knitr::opts_chunk$get("fig.path")), dev = c("png"))

```

```{r load, warning = FALSE, message = FALSE, include = FALSE}
#Libraries
library(BayesFactor)
library(tidyverse)

set.seed(20230703)
```

In the first section <span style="color: blue;">*[1] Loading subdatasets*</span> we load the `conf_subdata.rda` file, which includes an image of the environment with all subdatasets generated from the `50_subdatasets.R` code.

```{r [1]-Loading-subdatasets}

###[0] Loading subdatasets------------------------------------------------------

load(file="./05_analysis/subdata/conf_subdata.rda")


```

In section <span style="color: blue;">*[2] Testing log-transformation*</span> we run additional analyses regarding the log-10 transformation of the light data. After realizing that the linear light data violate the assumptions of linear regression models, (see Suppl. Figure 2 B, C and E) we generated log10-transformed light variables with which the requirements were approximately met (see Suppl. Figure 3). Here, we additionally tested whether the transformation improved the fit in the LMM, comparing the model with log10 transformation against a null model with linear light data in the same procedure as our hypothesis tests specified in the pre-registered analysis. The BF10 clearly shows evidence in favour of log10-transformation.

```{r [2]-Testing-log10-transformation}

###[2] Testing-log10-transformation---------------------------------------------------

# comparing model fit log10 vs. linear mEDI
#computing BF10: likelihood ratio of full model vs. null model
# including Field data only


#full model (numerator) log10-transformed
set.seed(20230703) 
CH1blog_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id  + sex,
                         data = Fielddata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)
#null model (denominator) linear (no transformation)
set.seed(20230703) 
CH1blog_denominator <- lmBF(diameter_3d ~ Mel_EDI + age + id + sex, 
                            data = Fielddata, 
                            whichRandom = c("id","sex"),
                            progress = FALSE, 
                            posterior = TRUE,
                            iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH1blog <-compare(CH1blog_numerator, CH1blog_denominator)

summary(BF_CH1blog)


```

In code section <span style="color: blue;">*[3] Positive control tests*</span> we test our confirmatory hypotheses in the controlled laboratory conditions as positive control tests. You find the results of these tests in Supplementary Tables 6  for the 75% data loss threshold sample (n=83) and in Supplementary Table 7 in the 50% data loss" threshold sample (n=63).

First, we tested hypothesis CH1 with the linear models specified in stage 1 of our report with data from our laboratory conditions (subdataset "Labdata"). The models are tested with log10-transformed and linear (non-transformed) mEDI as a predictor.

```{r [3]-Positive-control-tests CH1}
###[3] Positive control tests---------------------------------------------------
# Positive control: CH1 in Lab data

#computing BF10: likelihood ratio of full model vs. null model
# including Laboratory data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
CH1a_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex,
                      data = Labdata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)
#null model (denominator) 
set.seed(20230703) 
CH1a_denominator <- lmBF(diameter_3d ~ age + id + sex, 
                         data = Labdata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH1a <- compare(CH1a_numerator, CH1a_denominator)

summary(BF_CH1a)




# Positive control: CH1 in Lab data

#computing BF10: likelihood ratio of full model vs. null model
# including Laboratory data only
#linear (non-transformed) light data

#full model (numerator)
set.seed(20230703) 
CH1ax_numerator<- lmBF(diameter_3d ~ Mel_EDI + age + id + sex,
                       data = Labdata, 
                       whichRandom = c("id","sex"),
                       progress = FALSE, 
                       posterior = TRUE,
                       iterations = 10000
)
#null model (denominator) 
set.seed(20230703) 
CH1ax_denominator <- lmBF(diameter_3d ~ age + id + sex, 
                          data = Labdata, 
                          whichRandom = c("id","sex"),
                          progress = FALSE, 
                          posterior = TRUE,
                          iterations = 10000
)

#comparison of full div. by null model

set.seed(20230703) 
BF_CH1ax <- compare(CH1ax_numerator, CH1ax_denominator)

summary(BF_CH1ax)

```

Secondly, we tested hypothesis CH2 with the linear models specified in stage 1 of our report with data from our laboratory conditions (subdataset "Labdata"). Note that under these conditions, the light units mEDI and photopic lux are somewhat dissociated (see Figure 5). Again, the test is once run for a model including the log10-transformed light data (mEDI and photopic illuminance) and once with non-transformed light data.

```{r [3]-Positive-control-tests CH2}

# Positive control: CH2 in Lab data

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
CH2a_numerator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, 
                       data = Labdata, 
                       whichRandom = c("id","sex"), 
                       progress = FALSE, 
                       posterior = TRUE,
                       iterations = 10000
)

#null model (denominator) 
set.seed(20230703) 
CH2a_denominator <- lmBF(diameter_3d ~ log_phot_lux + age + id + sex, 
                         data = Labdata,
                         whichRandom = c("id","sex"), 
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH2_lab <- compare(CH2a_numerator, CH2a_denominator)


summary(BF_CH2_lab)


# Positive control: CH2 in Lab data

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#linear (non-transformed) light data

#full model (numerator)
set.seed(20230703) 
CH2ax_numerator <- lmBF(diameter_3d ~ Mel_EDI + age + id + sex, 
                        data = Labdata, 
                        whichRandom = c("id","sex"), 
                        progress = FALSE, 
                        posterior = TRUE,
                        iterations = 10000
)
#null model (denominator) 
set.seed(20230703) 
CH2ax_denominator <- lmBF(diameter_3d ~ phot_lux + age + id + sex, 
                          data = Labdata,
                          whichRandom = c("id","sex"), 
                          progress = FALSE, 
                          posterior = TRUE,
                          iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH2x_lab <- compare(CH2ax_numerator, CH2ax_denominator)

summary(BF_CH2x_lab)

```

Lastly, we test our age hypothesis CH3 in the data from the 10-minute dark adaptation (subdataset "Darkdata") as a positive control, where we expected the age effect to be most pronounced. In the tested models, no light variables are used as a predictor because these samples were taken in darkness, where the light measurements are not valid.

```{r [3]-Positive-control-tests CH3}

# Positive control: CH3 in Dark data


#computing BF10: likelihood ratio of full model vs. null model
# including Dark adapation data only
#linear (non-transformed) light data

#full model (numerator)
set.seed(20230703) 
CH3c_numerator<- lmBF(diameter_3d ~  age + id + sex, data = Darkdata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)

#null model (denominator) 
set.seed(20230703) 
CH3c_denominator <- lmBF(diameter_3d ~  id + sex, data = Darkdata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH3c <-  compare(CH3c_numerator, CH3c_denominator)


summary(BF_CH3c)

```

In the code given in <span style="color: blue;">*[4] Hypothesis testing - CH1*</span> , we test our confirmatory hypothesis CH1 in the data from the field condition (subdataset "Fielddata"). First, we conduct the test  with models including the log10-transformed mEDI predictor and then secondly with the linear mEDI predictor.

<span style="color: green;">*CH1: In real-world conditions, light-adapted pupil size changes as a function of melanopsin sensitivity-weighted retinal illumination with higher illumination associated with a smaller pupil size.*</span>


```{r [4]-Hypothesis-testing:-CH1-log10-transformed}
### [4] Hypothesis testing - CH1---------------------------------------------------
#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
CH1b_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex,
                      data = Fielddata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH1b_denominator <- lmBF(diameter_3d ~ age + id + sex, 
                         data = Fielddata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH1b <- compare(CH1b_numerator, CH1b_denominator)

summary(BF_CH1b)


```

CH1 test with the linear (non-transformed) melanopic Equivalent Daylight Illuminance (mEDI) predictor:


```{r [4]-Hypothesis-testing:-CH1-linear-data}

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#linear  light data (no log10 transformation)

#full model (numerator)
set.seed(20230703) 
CH1bx_numerator<- lmBF(diameter_3d ~ Mel_EDI + age + id + sex,
                      data = Fielddata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH1bx_denominator <- lmBF(diameter_3d ~ age + id + sex, 
                         data = Fielddata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
BF_CH1bx <-compare(CH1bx_numerator, CH1bx_denominator)

summary(BF_CH1bx)


```

In the code given in <span style="color: blue;">*[5] Hypothesis testing - CH2*</span> , we test our confirmatory hypothesis CH2 in the data from the field condition (subdataset "Fielddata"). First, we conduct the test  with models including the log10-transformed mEDI and photopic illuminance predictors and then secondly with the linear mEDI and photopic illuminance predictors.
 
<span style="color: green;">*CH2: In real-world conditions, melanopsin sensitivity-weighted retinal illumination better predicts pupil size than the weighted sum of L- and M-cone weighted retinal illumination (CIE 1931 Y, photopic illuminance).*</span>


```{r [5]-Hypothesis-testing:-CH2-log10-transformed}

 
 ### [5] Hypothesis testing - CH2----------------------------------------------------

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
CH2b_numerator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, 
                       data = Fielddata, 
                       whichRandom = c("id","sex"),
                       progress = FALSE, 
                       posterior = TRUE,
                       iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH2b_denominator <- lmBF(diameter_3d ~ log_phot_lux + age + id + sex, 
                         data = Fielddata,
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)
#comparison of full div. by null model
set.seed(20230703) 
BF_CH2b <- compare(CH2b_numerator, CH2b_denominator)

summary(BF_CH2b)


```

CH2 test with the linear (non-transformed) melanopic Equivalent Daylight Illuminance (mEDI) and photopic illuminance predictors:

```{r [5]-Hypothesis-testing:-CH2-linear-data}

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#linear  light data (no log10 transformation)

#full model (numerator)
set.seed(20230703) 
CH2bx_numerator <- lmBF(diameter_3d ~ Mel_EDI + age + id + sex, 
                       data = Fielddata, 
                       whichRandom = c("id","sex"), 
                       progress = FALSE, 
                       posterior = TRUE,
                       iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH2bx_denominator <- lmBF(diameter_3d ~ phot_lux + age + id + sex, 
                         data = Fielddata,
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)
#comparison of full div. by null model
set.seed(20230703) 
BF_CH2bx <- compare(CH2bx_numerator, CH2bx_denominator)

summary(BF_CH2bx)


```

To double check that our tests conducted with the "BayesFactors" package were valid, we additionally ran a test comparing the two models defined with a function from the *lme4* & *lmerTest* packages ("lmer") and compared the two models from CH2 regarding their Bayesian Information Criterion (BIC). The resulting BIC value for the full model is lower for the full model than with the null model, confirming the results from the BayesFactor analysis. However, the BIC test with using models with the non-transformed light data result in the following warning: <span style="color: red;">*"fit warnings: Some predictor variables are on very different scales: consider rescaling"*</span>. This further confirms the suggestion to use log10-transformed light data  instead of linear light data as predictors in linear regression. 

We then approximated the the Bayes factors from BICs computed in the *lme4* package using the  equation by Wagenmakers (2007), retrieved from [Stevens (2019)](https://osf.io/eszbd), resulting in very similar Bayes Factor magnitudes.

```{r [5]-Hypothesis-testing:-CH2-BIC-validation, warning=TRUE}
#loading required packages
library(lme4)
library(lmerTest)

 #Testing the models against each other with BICs from the lm4e package
#these tests are only used as a double check to 
#"validate" our procedure with the BayesFactor package 

#formulate models with lmerTest package
set.seed(20230703) 
(CH2_NHST_H1<-lmer(diameter_3d ~ log_Mel_EDI + age + (1|id) + (1|sex), Fielddata))

set.seed(20230703) 
(CH2_NHST_H0<-lmer(diameter_3d ~ log_phot_lux + age + (1|id) + (1|sex), Fielddata))

#compute a model comparison with Bayesian information criterion
# the lower the BIC, the better the model fit
set.seed(20230703) 
BIC_CH2<- BIC(CH2_NHST_H0,CH2_NHST_H1)
BIC_CH2
#BIC is lower with log10(mEDI) than with log10(photopic lux)

#Approximating Bayes factors from BICs using the  equation by Wagenmakers (2007),
#retrieved from Stevens (2019) https://osf.io/eszbd

#function for converting BICs into BFs (retrieved from Stevens (2019) https://osf.io/eszbd )
bic_bf10 <- function(null, alternative) {
  new_bf <- exp((null - alternative) / 2) # convert BICs to Bayes factor
  names(new_bf) <- NULL # remove BIC label
  return(new_bf) # return Bayes factor of alternative over null hypothesis
}

#compute BIC for each model of CH2 defined earlier
set.seed(20230703) 
CH2_H1_bic<- BIC(CH2_NHST_H1)

set.seed(20230703) 
CH2_H0_bic<- BIC(CH2_NHST_H0)


set.seed(20230703) 
#convert the BICs into an approximated BF10 factor
bic_bf10(CH2_H0_bic,CH2_H1_bic)
#result very similar to the BF10 computed with BayesFactor package.

# Repeating the BIC test using the non-log10 transformed light intensity vars
set.seed(20230703) 
(CH2_NHST_nolog_H1<-lmer(diameter_3d ~ Mel_EDI + age  + (1|id) + (1|sex), Fielddata))

set.seed(20230703) 
(CH2_NHST_nolog_H0<-lmer(diameter_3d ~ phot_lux + age + (1|id) + (1|sex), Fielddata))

set.seed(20230703)
BIC(CH2_NHST_nolog_H0, CH2_NHST_nolog_H1)

#with the non-transformed light data the following warning pops up:
#"fit warnings:
#Some predictor variables are on very different scales: consider rescaling"
#--> this again comes back to linear assumptions being violated without log10-transformation
#regardless, the model with log10(mEDI) (H1) has a lower BIC and is preferred.


#compute BIC for each model of CH2 without log10 transformation
set.seed(20230703) 
CH2_H1_nolog_bic<- BIC(CH2_NHST_nolog_H1)
set.seed(20230703) 
CH2_H0_nolog_bic<- BIC(CH2_NHST_nolog_H0)

set.seed(20230703) 
#convert the BICs into an approximated BF10 factor
bic_bf10(CH2_H0_nolog_bic,CH2_H1_nolog_bic)
#results very similar to the BF10 computed with BayesFactor package.


```

In the code given in <span style="color: blue;">*[6] Hypothesis testing - CH3*</span> , we test our confirmatory hypothesis CH3 in the data from the field condition (subdataset "Fielddata"). First, we conduct the test  with models including the log10-transformed mEDI  predictor and then secondly with the linear mEDI predictor.
 
<span style="color: green;">*CH3: In real-world conditions, light-adapted pupil size changes as a function of age, with higher age associated with a smaller pupil size.*</span>

```{r [6] Hypothesis-testing:-CH3-log10-transformed}

### [6] Hypothesis testing - CH3-------------------------------------------------------------------------
#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
CH3b_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, data = Fielddata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH3b_denominator <- lmBF(diameter_3d ~ log_Mel_EDI + id + sex, data = Fielddata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)
#comparison of full div. by null model
set.seed(20230703) 
BF_CH3b <-  compare(CH3b_numerator, CH3b_denominator)

summary(BF_CH3b)

```

CH3 test with the linear (non-transformed) melanopic Equivalent Daylight Illuminance (mEDI) predictor:


```{r [6] Hypothesis-testing:-CH3-linear-data}

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#linear  light data (no log10 transformation)

#full model (numerator)
set.seed(20230703) 
CH3bx_numerator<- lmBF(diameter_3d ~ Mel_EDI + age + id + sex, data = Fielddata, 
                      whichRandom = c("id","sex"),
                      progress = FALSE, 
                      posterior = TRUE,
                      iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
CH3bx_denominator <- lmBF(diameter_3d ~ Mel_EDI + id + sex, data = Fielddata, 
                         whichRandom = c("id","sex"),
                         progress = FALSE, 
                         posterior = TRUE,
                         iterations = 10000
)
#comparison of full div. by null model
set.seed(20230703) 
BF_CH3b_nolog <-  compare(CH3bx_numerator, CH3bx_denominator)

summary(BF_CH3b_nolog)


```
 
In the code section <span style="color: blue;">*[7] Exploratory analyses - EH*</span> we analyse our exploratory analyses specified in the Stage 2 RR manuscript. The analysis procedure corresponds to the confirmatory hypotheses. However, we only include log10-transformed mEDI as a predictor in these cases.

- *EH1: Sex differences in light-adapted pupil size are present under real-world conditions.*
- *EH2: Light-adapted pupil size varies as a function of iris colour under real-world conditions.*
- *EH3: Light-adapted pupil size varies as a function of habitual caffeine consumption (relative to body weight) under real-world conditions.*
- *EH4: Light-adapted pupil size varies as a function of the acute caffeine consumption (relative to body weight) under real-world conditions.*

Sex differences:
 
```{r [7]-Exploratory-analyses: sex differences}
 
### [7] Exploratory analyses - EH-----------------------------------------------

# Sex differences 

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
sexdif_field_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, 
                              data = Fielddata, 
                              whichRandom = c("id","sex"),
                              progress = FALSE, 
                              posterior = TRUE,
                              iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
sexdif_field_denominator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id,
                                 data = Fielddata, 
                                 whichRandom = c("id","sex"),  
                                 progress = FALSE, 
                                 posterior = TRUE,
                                 iterations = 10000
)
#comparison of full div. by null model
set.seed(20230703) 
sexdif_field <- compare(sexdif_field_numerator, sexdif_field_denominator)

summary(sexdif_field)


# strong evidence for the null model

```

Caffeine consumption:

```{r [7]-Exploratory-analyses: caffeine consumption}

#Caffeine consumption-

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
caf_field_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex + acute_sum_rel,
                           data = Fielddata, 
                     whichRandom = c("id","sex"),
                     progress = FALSE, 
                     posterior = TRUE,
                     iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
caf_field_denominator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, 
                              data = Fielddata, 
                              whichRandom = c("id","sex"),
                              progress = FALSE, 
                              posterior = TRUE,
                              iterations = 10000
)

#comparison of full div. by null model

set.seed(20230703) 
caf_field <- compare(caf_field_numerator, caf_field_denominator)

summary(caf_field)

# --> moderate evidence for null model 


#habitual caffeine in the field data


#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
hcaf_field_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age  + id + sex + habitual_sum_rel, 
                            data = Fielddata, 
                          whichRandom = c("id","sex"),
                          progress = FALSE, 
                          posterior = TRUE,
                          iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
hcaf_field_denominator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex, 
                               data = Fielddata, 
                               whichRandom = c("id","sex"),
                             progress = FALSE, 
                             posterior = TRUE,
                             iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
hcaf_field<- compare(hcaf_field_numerator, hcaf_field_denominator)

summary(hcaf_field)

# moderate evidence for null model 

```

Iris colour:

```{r [7]-Exploratory-analyses: iris colour}
# iris colour 

#computing BF10: likelihood ratio of full model vs. null model
# including Field data only
#log10-transformed light data

#full model (numerator)
set.seed(20230703) 
iris_field_numerator<- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex + iris_colour, 
                            data = Fielddata, 
                          whichRandom = c("id","sex", "iris_colour"),
                          progress = FALSE, 
                          posterior = TRUE,
                          iterations = 10000
)
#null model (denominator)
set.seed(20230703) 
iris_field_denominator <- lmBF(diameter_3d ~ log_Mel_EDI + age + id + sex,
                               data = Fielddata, 
                               whichRandom = c("id","sex", "iris_colour"),
                             progress = FALSE, 
                             posterior = TRUE,
                             iterations = 10000
)

#comparison of full div. by null model
set.seed(20230703) 
iris_field <- compare(iris_field_numerator, iris_field_denominator)

summary(iris_field)

# strong evidence for null model 

```
