---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This code was (not) straightforward to codecheck.
[... ADD MORE INTERESTING FINDINGS HERE..]

\clearpage

# CODECHECKER notes

This project was created in R.  The README of the project provided a
comprehensive overview of the structure of the project, and the steps
required to reproduce the figures.  Another highlight of the project
structure was its use of the renv package to explicitly state which R
packages (and their versions) should be installed.  The call to
`renv::update()` in the project root took approximately 30 minutes on
my laptop to install the 199 packages.

Once the packages were installed, the steps involved were fairly
straightforward -- all assuming the working directory was the root of
the project.

As noted however in the README, when running the code on a mac (as I
was), `device=cairo_pdf` arguments needed deleting (from files
`40_demographics.R` and `52_figures&tables.R`).  The code was then
evaluated in the following logical order:

```{r,eval=FALSE}
source("01_surveydata/10_surveydata_prep.R")
source("02_rawdata/20_rawdata_import.R")
source("02_rawdata/21_qualitychecks.R")
source("02_rawdata/22_categorisation.R")
source("03_datamerge/30_datamerge.R")
source("04_demographics/40_demographics.R")
source("05_analysis/50_subdatasets.R")
source("05_analysis/51_hypotheses.R")
source("05_analysis/52_figures&tables.R")
```

The output files were placed in the `06_output` folder.



## Recommendations

1. As the code can all be run without any interaction, I would suggest
making a simple (shell or R) script that deletes any intermediate
files, and then evaluates all the steps in the correct order.  

2. The code generates many warnings, mostly caused when packages are
   loaded.  It might be helpful to silence those warnings that can
   safely be ignored.
   
3. Unless the argument `device=cairo_pdf' is necessary on a particular
   platform, I'd suggest deleting that call from your scripts so that
   they are more portable.  (Alternatively, include comnditionals
   based on the operating system to    check whether the device
   parameter can be included.)




\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

I would like to thank the authors for promptly answering any queries I
had with this reproduction.  CODECHECK was financially supported by the
Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
